A generalized definition of multidimensional item response theory parameters

### 2023-03-10 output/paper_draft/paper_M2PLM_parameters.Rmd
Moves the "Test space" section before (temptatively)
Adds minor relevant cross-mention
Changes the "test space" section according to its precedence and the derivation based on the invariance of the M2PL model.

@@

As Equation \@ref(eq:M2PL-formula-polar) shows, the inner product matrix is
involved in the expression of the model in polar coordinates.
Importantly, this shows that @reckase_difficulty_1985's Equation 3 (p. 403)
already assumes the orthonormality of the latent space.

@@

\begin{equation}
  `r DISCR_VECTOR_STD_EQ`                                (\#eq:discr-vector-std)
\end{equation}

@@

Substituting $`r DIR_COS_ITEM_VEC_STD`$
(Equation \@ref(eq:direction-cosine-vectors-eq)) and
$`r DISCR_VECTOR_STD`$ (Equation \@ref(eq:discr-vector-std))
by their respective expressions results in the
expression for the direction cosine vector of item $i$ in $`r LATENT_SPACE`$,

@@

## Test space and latent space

Before defining the multidimensional parameters, we need to make a clarification
regarding the representation of the items in the latent space.
We call $`r TEST_SPACE`$ the *test space* [@zhang_theoretical_1999] of
the discrimination vectors.
This space is where the item vectors can be properly represented.
It is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.
Let's consider the model given by Equation \@ref(eq:M2PL-formulation),
where the latent traits and the parameters $`r DISCR_VECTOR`$ are expressed
in the same basis $`r LS_BASIS`$ in their respective spaces.

Since the response probability must be invariant, because of Equation
\@ref(eq:change-basis), parameter $`r DISCR_VECTOR`$ must also be transformed
in $`r DISCR_VECTOR_STD`$.
Equating the probabilities we get $a_1^{'}=P^{-1^T}a_i=M^{-1}Pa_i$ .
This shows that first a basis change to the standard base is performed and then
a transformation through $`r INNER_PROD_MATRIX_INV`$,
so the $`r DISCR_VECTOR_STD`$ are expressed in the standard basis.

\begin{equation}
  `r DISCR_VECTOR_MODULE_EQ`                     (\#eq:discr-param-squared-norm)
\end{equation}

Therefore, in the test space, an inner product matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined such that $`r INNER_PROD_DISCR_EQ`$,
to keep the norm invariant.
With this definition we have that

>>>>

### Test space and latent space

Before proceeding further, we need to make a clarification
regarding the representation of the items in the latent space.
Let's consider the model given by Equation \@ref(eq:M2PL-formulation),
where the latent traits and the parameters $`r DISCR_VECTOR`$ are expressed
in the same basis $`r LS_BASIS`$ in their respective spaces.
The coordinates of $`r DISCR_VECTOR`$ are then $`r DISCR_COORDS`$.
Since the response probability must be invariant with respect to
a change of basis, $`r DISCR_COORDS`$ must also be transformed
into $`r DISCR_STD_COORDS`$, such that $`r INVARIANCE_EQ`$;
therefore, $`r DISCR_STD_COORDS_EQ`$.
This shows that first a transformation through $`r INNER_PROD_MATRIX_INV`$
is performed and then a change to the standard basis,
so the $`r DISCR_STD_COORDS`$ are expressed in the standard basis.
The norm of $`r DISCR_VECTOR`$ must then fulfill

\begin{equation}
  `r DISCR_VECTOR_MODULE_EQ`.                    (\#eq:discr-param-squared-norm)
\end{equation}

Therefore, an inner product $`r ITEM_SPACE_INNER_PROD`$ with Gram matrix
$`r INNER_PROD_MATRIX_INV`$ can be defined, such that $`r INNER_PROD_DISCR_EQ`$
keeps the norm of $`r DISCR_VECTOR`$ invariant.
The discrimination vectors are thus represented in their own space
$`r TEST_SPACE`$ with basis $`r ITEM_SPACE_BASIS`$,
which we refer to as the *test space* [@zhang_theoretical_1999].
The test space is in general different from the latent space $`r LATENT_SPACE`$,
although there is a bijective relationship between the two sets of spaces.

### Direction cosines in the latent space

@@

As Equation \@ref(eq:M2PL-formula-polar) shows, the inner product matrix is
involved in the expression of the model in polar coordinates.
Importantly, this shows that @reckase_difficulty_1985's Equation 3 (p. 403)
already assumes the orthonormality of the latent space, as we stated before.

@@

\begin{equation}
  `r DISCR_STD_COORDS_EQ`                                (\#eq:discr-vector-std)
\end{equation}

@@

Substituting $`r DIR_COS_ITEM_VEC_STD`$
(Equation \@ref(eq:direction-cosine-vectors-eq)) and
$`r DISCR_STD_COORDS`$ (Equation \@ref(eq:discr-vector-std))
by their respective expressions results in the
expression for the direction cosine vector of item $i$ in $`r LATENT_SPACE`$,

@@

In the test space we have that
